Planar Maximal Covering with Ellipses

### 2019-05-05 quali/quali.presentation/slides.tex
WIP

\begin{frame}{Maximum Weight Clique Problem}{Algorithm}
	For a disk $D_i$, a counter-clockwise traversal visits every $\Gamma_+(i,j)$ and $\Gamma_-(i,j)$ in counter-clockwise order.

@@

		\item The arc $\Gamma_+(i,j),\Gamma_-(i,j)$ (counter-clockwise) determines a region where $i$ and $j$ intersect.

		\item In a counter-clockwise traversal, the arcs where $\Gamma_+(i,j) > \Gamma_-(i,j)$ can be a problem for the implementation. The traversal is on a circle, where to start?

		\item If the traversal reaches a opening angle, we mark the intersecting disk as active. If it reaches a closing angle we unmark it.

		\item We want to find a point in the traversal with the most active disks.
	\end{itemize}
\end{frame}

@@

	For every disk, traverse the sorted list of intersection angles twice, keeping a set of active disks, and the current best solution.

	Doing the traversal twice solves the problem of deciding where to start.

@@

	\caption{The intersections list of a disk with three other disks.}
	\input{figures/fig:array_disks.tex}
	\source{Elaborated by the author.}
	\label{fig:array_disks}
\end{figure}
\end{frame}

@@

		\item It can be implemented in $K\log{n}$ where $K$ is the number of intersections \autocite{bentley:1979}.
	\end{itemize}

>>>>

	Some observations allow us to arrive at the algorithm:

%	For a disk $D_i$, a counter-clockwise traversal visits every $\Gamma_+(i,j)$ and $\Gamma_-(i,j)$ in counter-clockwise order.

@@

		\item The arc $A(\Gamma_+(i,j),\Gamma_-(i,j))$ (counter-clockwise) determines a region where $i$ and $j$ intersect.

		\item For every disk $D_i$, we want to find an angle $\theta$, such that $$w(\{D_k : \theta \in A(\Gamma_+(i,k),\Gamma_-(i,k))\}),$$ is maximized. Most overlapping intervals (circular).

		\item To transform it to the problem of finding the most overlapping intervals, just copy the list of intersection angles. The arcs such that $\Gamma_+(i,j) > \Gamma_-(i,j)$ will be considered.
	\end{itemize}
\end{frame}

@@

	Transforming it to the most overlapping intervals.

@@

		\caption{The intersections list of a disk with three other disks.}
		\input{figures/fig:array_disks.tex}
		\source{Elaborated by the author.}
		%\label{fig:array_disks}
	\end{figure}
\end{frame}

\begin{frame}{Maximum Weight Clique Problem}{Algorithm}
	Our algorithm for the Maximum Weight Clique Problem:\\~\\

	For every disk $D_i$, do:
	\begin{itemize}
		\item Get the sorted list of intersection angles with $D_i$
				$A=\cap_{j}\Gamma_+(i,j) \cup \Gamma_-(i,j)$.
		\item Traverse it twice starting at the angle with smallest value.
		\begin{itemize}
			\item Keep a set of active disks. When an opening angle is visited, make the disk active, otherwise remove it from the set.
			\item Update the optimal solution. Use the closing angle.
		\end{itemize}
	\end{itemize}
\end{frame}

@@

		\item It can be implemented in $K\log{n}$ where $K$ is the number of intersections \autocite{bentley:1979}.

		\item The algorithm is basically finding the most number of overlapping intervals $n$ times.

		\item As it was mentioned, the solution found by this algorithm is a solution for the Maximal Covering by One Disk.
	\end{itemize}
